TBD

### 2016-09-28 paper.tex
LINCAL

Moreover,
\begin{equation}
n_{j,pq} = (\delta_{p}^{j}\vee\delta_{q}^{j}) v_{pq} 
\end{equation}

fiducial initial guess

The following partial derivatives are now easily computed

\begin{eqnarray}
\frac{c_{ij}}{\partial \eta_i} &=& y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\ 
\frac{c_{ij}}{\partial \varphi_i} &=&  -i y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\
\frac{c_{ij}}{\partial \eta_j} &=& y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\ 
\frac{c_{ij}}{\partial \varphi_j} &=&  i y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\
\frac{y_{i-j}}{\partial \varphi_j} &=&  e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}
\end{eqnarray}

The Wirtinger derivative is used in the last equation.

\begin{eqnarray}
c_{ij} &\approx& c_{ij}^0 + \Delta \eta_i(y_{i-j}^0 e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}) + \Delta \eta_j(y_{i-j}^0 e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
&& -i\Delta\varphi_i (y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}) +i\Delta\varphi_j (y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
&& y_{i-j}^1(y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
&\approx&  c_{ij}^0 + e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_i+ \Delta \eta_j - i\Delta\varphi_i + i\Delta\varphi_i))
\end{eqnarray}

\begin{equation}
\label{eq:residual}
r_{ij} = \delta_{ij} = c_{ij}-c_{ij}^0 = e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_i+ \Delta \eta_j - i\Delta\varphi_i + i\Delta\varphi_i)) 
\end{equation}

Eq.~\ref{eq:residual} allows us to construct the following linear system:

\begin{equation}
\boldsymbol{J}[\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = \boldsymbol{r}, 
\end{equation}

where $\boldsymbol{J}$ is equal to 
\begin{equation}
\boldsymbol{J} = \bigg [\overbrace{\frac{c_{pq}}{\partial \eta_i}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial \varphi_i}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial y_{t}}}^{t=1\cdots r_s} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q) 
\end{equation}
or
\begin{equation}
\boldsymbol{J} = \bigg [\frac{c_{pq}}{\partial \boldsymbol{\eta}},~\frac{c_{pq}}{\partial \boldsymbol{\varphi}},~\frac{c_{pq}}{\partial \boldsymbol{y}} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q). 
\end{equation}

The last column is again a Wirtinger derivative.

Which means we can obtain the least-squares estimate as follows:

\begin{equation}
[\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = [\boldsymbol{J}^H\boldsymbol{J}]^{-1}\boldsymbol{J}^H\boldsymbol{r}.
\end{equation}

>>>>

\begin{eqnarray}
\bM &=& 
\begin{bmatrix}
\coolover{\!\!\!\!\!\!\!{\scriptstyle j=1,\ldots,L}}{\frac{\partial v_{pq}}{\partial \widetilde{\eta}_j}} & \coolover{\!\!\!\!{\scriptstyle k=1,\ldots,L}}{~\frac{\partial v_{pq}}{\partial \widetilde{\varphi}_k}}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\frac{\partial v_{ij}}{\partial \eta_j}}{\scriptstyle [pq] = 1,\ldots,B~(p<q)}
\end{matrix}\\
&=& \begin{bmatrix}
\coolunder{\!\!\!\!\!\!\!{\scriptstyle j=1,\ldots,N}}{m_{j,pq}} & \coolunder{\!\!\!\!{\scriptstyle k=1,\ldots,N}}{i m_{k,pq}}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\frac{\partial v_{ij}}{\partial \eta_j}}{\scriptstyle [pq] = 1,\ldots,B~(p<q)}
\end{matrix}\\
\end{eqnarray}

Moreover,
\begin{equation}
n_{j,pq} = (\delta_{p}^{j}\vee\delta_{q}^{j}) v_{pq} 
\end{equation}
and
\begin{equation}
m_{j,pq} = \delta_{\phi_{pq}}^{j} v_{pq}.
\end{equation}

% fiducial initial guess 
% 
% The following partial derivatives are now easily computed
% 
% \begin{eqnarray}
% \frac{c_{ij}}{\partial \eta_i} &=& y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\ 
% \frac{c_{ij}}{\partial \varphi_i} &=&  -i y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\
% \frac{c_{ij}}{\partial \eta_j} &=& y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\ 
% \frac{c_{ij}}{\partial \varphi_j} &=&  i y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\
% \frac{y_{i-j}}{\partial \varphi_j} &=&  e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}
% \end{eqnarray}
% 
% 
% The Wirtinger derivative is used in the last equation.
% 
% \begin{eqnarray}
% c_{ij} &\approx& c_{ij}^0 + \Delta \eta_i(y_{i-j}^0 e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}) + \Delta \eta_j(y_{i-j}^0 e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
% && -i\Delta\varphi_i (y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}) +i\Delta\varphi_j (y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
% && y_{i-j}^1(y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
% &\approx&  c_{ij}^0 + e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_i+ \Delta \eta_j - i\Delta\varphi_i + i\Delta\varphi_i))
% \end{eqnarray}
% 
% \begin{equation}
% \label{eq:residual}
% r_{ij} = \delta_{ij} = c_{ij}-c_{ij}^0 = e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_i+ \Delta \eta_j - i\Delta\varphi_i + i\Delta\varphi_i)) 
% \end{equation}
% 
% Eq.~\ref{eq:residual} allows us to construct the following linear system:
% 
% \begin{equation}
% \boldsymbol{J}[\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = \boldsymbol{r}, 
% \end{equation}
% 
% where $\boldsymbol{J}$ is equal to 
% \begin{equation}
% \boldsymbol{J} = \bigg [\overbrace{\frac{c_{pq}}{\partial \eta_i}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial \varphi_i}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial y_{t}}}^{t=1\cdots r_s} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q) 
% \end{equation}
% or
% \begin{equation}
% \boldsymbol{J} = \bigg [\frac{c_{pq}}{\partial \boldsymbol{\eta}},~\frac{c_{pq}}{\partial \boldsymbol{\varphi}},~\frac{c_{pq}}{\partial \boldsymbol{y}} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q). 
% \end{equation}
% 
% The last column is again a Wirtinger derivative.
% 
% Which means we can obtain the least-squares estimate as follows:
% 
% \begin{equation}
% [\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = [\boldsymbol{J}^H\boldsymbol{J}]^{-1}\boldsymbol{J}^H\boldsymbol{r}.
% \end{equation}
